---
title: "Analyses of the Immune Microenvironment"
---

```{r message=FALSE, warning=FALSE, include=FALSE}
source("../PrecisionMed/scFunctions.R")
```

# Purpose and rationale

In the bulk POG pipeline, patients are assessed for eligibility for immune checkpoint inhibitors. One of the criteria for eligibility is the abundance of CD8+ T-cells, which is inferred from bulk transcription data using CIBERSORT. 

# Table of Contents

1. [Immune cell composition](#immune-cell-composition)
2. [Correlation with CIBERSORT scores]()
3. [Presence of T-cell subtypes]()
4. [T-cell composition of immunological samples]()

# Immune cell composition

```{r}
# t-cells from all of the samples
tCells_seuList <- readRDS("../PrecisionMed/Data/singleTcells.RDS")
```



# Correlation with CIBERSORT scores


# Presence of T-cell subtypes

Cell types of interest:

- CD8+ T-cells 
- Trm (CD39+CD103+CD8+): Associated with [...]
- Treg (CD4+FOXP3+): [...]

```{r}

```

## Changes in composition across biopsies

```{r}

```

# T-cell composition of immunological samples

